Draft-assinment1

### 2017-02-21 Draft-xuezhou-sjb.Rmd

>>>>

Through the process of summarizing these variables and analyzing the relationship between these variables, we found that for federally aided students in most colleges, around half of the students' parents did not complete the college.The average net price costs for most institutuins are falling into the range between $16000 - $20000. Among the 7703 institution samples, more than 50% of the students are able to receive Pell Grant or Federal Loans as means of finanical support, and on average, 60% of students are financial independent. In most colleges, the students are able to reach the family income between $12000 and $18000.

We also found that California has the most universities across the nation, with 797 institutions. In terms of predominant degree offered, 43.2% are classified as Certificate-degree predominant institution, which is the most predominant type.

Our findings also suggest that the Title IV institions located in DC, VT, MA, NH, RI have a relative high amount of average net costs than those in other states. The students in private non-profit institutions and public institutions are less likely to seek Pell Grant as financial assistance than the students in the private for-profit colleges.In most private for-profit colleges, the students are more likely to be financial independet.

It is also indicated that there exists a negative correlation between the percentage of students who receive Pell Grant and the students median family income after they graduate: for institutions with low percentage of students who receive the Pell Grant, the financial aids like Pell Grant may not be as necessary as they are in the instituions with high value of PCTPELL, thus these collges students will tend to have a high median family income after they graduate.

As to the factors that influence post-graduate earning, we explore the relationship between median earning six years from entry and amount of debt, default rate for student loan and predominant degree type. The analysis suggests that there is a positive relationship between the median debt amount for students who have not completed and post-graduation earnings. This may be due to the fact that top universities usually have tuitions but may also indicates that students who are willing to take more debts for their college education are likely to make more money after graduation. In addition, default rate of student loan is negatively related to post-graduate earning. This finding is reasonable since students making more money are more likely to pay off their debt. The variable can be used a school-level predictor to predict overall post-graduate earning for each university. The degree type, unsurprisingly, has an impact on the earnings students are making after graduation. As the level of graduation increases, the post-graduate earning also increase significantly, which suggests that investing in education is worthwhile.

As a result of all the statistical analysis, we conclude that XXXXXXXXXXXX. Attributes such as               the students' post graudate earnings.
